Chlorophylla

### 2019-08-02 Chlorophyll.Rmd
chlorophyll

# Loading the data
load("Data/MODIS_Chloro.RData") # Extracted chlorophyll data
load("Data/SACTN_US.RData") # Site list of all the sites along the west coast

@@

match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                          query = as.matrix(SACTN_US[,5:6]), k = 1)

# Matching the sites within the chlorophyll data to the sites along the west coast
pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = SACTN_US$site)

>>>>

# Loading the data
load("Data/MODIS_Chloro.RData") # Extracted chlorophyll data
load("Data/site_list_sub.RData") # Site list of all the sites along the west coast

@@

match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
                          query = as.matrix(site_list_sub[,5:6]), k = 1)

# Matching the sites within the chlorophyll data to the sites along the west coast
pixel_match <- unique_pixel[match_index,] %>%
  unite(col = combi, lon, lat, sep = "/", remove = F) %>%
  mutate(site = site_list_sub$site)
